---
title: "Research Title"
subtitle: "A detailed investigation into [specific research question]"
author:
  - name: "First Author"
    orcid: "0000-0000-0000-0000"
    email: "first.author@university.edu"
    affiliations:
      - name: "Department of [Department], University of [Name]"
        address: "Address Line 1, City, Country"
  - name: "Second Author"
    orcid: "0000-0000-0000-0000"
    email: "second.author@university.edu"
    affiliations:
      - name: "Department of [Department], University of [Name]"
        address: "Address Line 1, City, Country"
date: today
abstract: |
  This study investigates [research question/problem]. Using [methodology], we analyzed [data/subjects] to examine [specific aspects]. Our findings reveal [key results]. These results suggest [implications] and contribute to [field of study] by [contribution]. The study has implications for [practical applications/future research].
keywords: ["keyword1", "keyword2", "keyword3", "keyword4", "keyword5"]
---

```{r}
#| label: setup
#| include: false

set.seed(42)
# Load required packages
library(ggplot2)
library(dplyr)
library(tidyr)
library(corrplot)

# Set global chunk options
knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 6,
  fig.align = "center",
  out.width = "80%",
  dpi = 300
)

# Set ggplot2 theme
theme_set(theme_minimal())
```

# Introduction

## Background and Rationale

The field of \[research area\] has seen significant developments in recent years [@citation2023]. However, several gaps remain in our understanding of \[specific topic\]. Previous research has shown that \[previous findings\] [@citation2022], but these studies have limitations including [limitations].

## Research Problem

The primary problem addressed in this study is \[problem statement\]. This issue is important because \[significance\]. Current approaches to \[problem area\] are insufficient due to \[reasons\].

## Research Questions and Hypotheses

This study addresses the following research questions:

1.  **RQ1**: \[First research question\]?
2.  **RQ2**: \[Second research question\]?
3.  **RQ3**: \[Third research question\]?

Based on existing literature, we hypothesize that:

-   **H1**: \[First hypothesis\]
-   **H2**: \[Second hypothesis\]
-   **H3**: \[Third hypothesis\]

## Objectives

The main objectives of this study are to:

1.  \[First objective\]
2.  \[Second objective\]
3.  \[Third objective\]

# Literature Review

## Theoretical Framework

### \[Theory/Model Name\]

The theoretical foundation for this study is based on \[theory name\] [@seminal_citation]. This theory posits that \[theory explanation\]. The key components of this framework include:

-   **Component 1**: \[Description\]
-   **Component 2**: \[Description\]
-   **Component 3**: \[Description\]

## Previous Research

### Studies on \[Topic Area 1\]

Research in [topic area] has primarily focused on [focus areas]. @author2023 found that [findings], while @another_author2022 demonstrated \[different findings\]. However, these studies were limited by [limitations].

### Studies on \[Topic Area 2\]

Recent investigations into \[topic area 2\] have revealed \[findings\] [@recent_citation]. The work by @researcher2023 is particularly relevant as it \[relevance\].

## Research Gaps

Despite the extensive research in this area, several gaps remain:

1.  **Gap 1**: \[Description of gap\]
2.  **Gap 2**: \[Description of gap\]
3.  **Gap 3**: \[Description of gap\]

# Methodology

## Research Design

This study employs a \[research design type\] design to investigate \[research focus\]. The design was chosen because \[justification\].

## Participants/Sample

### Sample Size and Power Analysis

Power analysis using G\*Power 3.1.9.7 indicated that a minimum sample size of \[n\] participants would be required to detect a medium effect size (Cohen's d = 0.5) with 80% power and $\alpha = 0.05$.

### Recruitment and Selection

Participants were recruited through \[recruitment method\]. Inclusion criteria were:

-   \[Criterion 1\]
-   \[Criterion 2\]
-   \[Criterion 3\]

Exclusion criteria included:

-   \[Exclusion 1\]
-   \[Exclusion 2\]

## Materials and Measures

### \[Instrument 1 Name\]

\[Description of instrument, reliability, validity information\]

### \[Instrument 2 Name\]

\[Description of instrument, reliability, validity information\]

## Procedure

The study procedure involved the following steps:

1.  **Pre-screening**: \[Description\]
2.  **Baseline assessment**: \[Description\]
3.  **Intervention/manipulation**: \[Description\]
4.  **Post-assessment**: \[Description\]
5.  **Follow-up**: \[Description\]

## Data Analysis Plan

Data analysis was conducted using R version `r R.version.string` [@R-base]. The analysis plan included:

### Descriptive Statistics

Descriptive statistics were calculated for all variables, including measures of central tendency, variability, and distribution shape.

### Inferential Statistics

The following analytical approaches were used:

-   **Primary analysis**: \[Statistical test\] to examine \[specific comparison\]
-   **Secondary analyses**: \[Additional tests\]
-   **Exploratory analyses**: \[Exploratory approaches\]

### Missing Data

Missing data patterns were examined and handled using \[approach\].

## Ethical Considerations

This study was approved by the \[Institution\] Institutional Review Board (IRB #\[number\]). All participants provided informed consent before participation. Data confidentiality and anonymity were maintained throughout the study.

# Results

```{r}
#| label: load-data
#| include: false

# Load data using targets
# tar_load(cleaned_data)
# tar_load(analysis_results)

# For template purposes, create sample data
sample_data <- data.frame(
  group = rep(c("Control", "Treatment"), each = 50),
  pre_score = rnorm(100, mean = 50, sd = 10),
  post_score = rnorm(100, mean = c(rep(52, 50), rep(58, 50)), sd = 10),
  age = rnorm(100, mean = 25, sd = 5),
  gender = sample(c("Male", "Female"), 100, replace = TRUE)
)
```

## Descriptive Statistics

### Sample Characteristics

The final sample consisted of N = `r nrow(sample_data)` participants. Sample characteristics are presented in @tbl-demographics.

```{r}
#| label: tbl-demographics
#| tbl-cap: "Sample Demographics"

# Create demographics table
demographics <- sample_data %>%
  summarise(
    N = n(),
    `Age M (SD)` = paste0(round(mean(age), 1), " (", round(sd(age), 1), ")"),
    `Female n (%)` = paste0(
      sum(gender == "Female"),
      " (",
      round(sum(gender == "Female") / n() * 100, 1),
      "%)"
    )
  )

knitr::kable(demographics)
```

### Descriptive Statistics by Group

@tbl-descriptives presents descriptive statistics for key variables by experimental condition.

```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive Statistics by Group"

# Create descriptives table
descriptives <- sample_data %>%
  group_by(group) %>%
  summarise(
    N = n(),
    `Pre-test M (SD)` = paste0(
      round(mean(pre_score), 2),
      " (",
      round(sd(pre_score), 2),
      ")"
    ),
    `Post-test M (SD)` = paste0(
      round(mean(post_score), 2),
      " (",
      round(sd(post_score), 2),
      ")"
    ),
    .groups = 'drop'
  )

knitr::kable(descriptives)
```

## Primary Analyses

### Research Question 1

To address RQ1, we conducted \[statistical test\]. Results indicated \[findings\]. @fig-main-results illustrates the primary findings.

```{r}
#| label: fig-main-results
#| fig-cap: "Main Results: Pre- and Post-test Scores by Group"

# Create main results figure
sample_data %>%
  pivot_longer(
    cols = c(pre_score, post_score),
    names_to = "time",
    values_to = "score"
  ) %>%
  mutate(time = ifelse(time == "pre_score", "Pre-test", "Post-test")) %>%
  ggplot(aes(x = time, y = score, fill = group)) +
  geom_boxplot(alpha = 0.7) +
  geom_point(
    position = position_jitterdodge(dodge.width = 0.75),
    alpha = 0.3,
    size = 0.8
  ) +
  labs(
    x = "Time Point",
    y = "Score",
    fill = "Group",
    title = "Pre- and Post-test Scores by Experimental Group"
  ) +
  theme_minimal() +
  scale_fill_brewer(type = "qual", palette = "Set2")
```

### Statistical Test Results

```{r}
#| label: statistical-tests

# Conduct statistical tests
t_test_result <- t.test(post_score ~ group, data = sample_data)

# Effect size calculation
library(effectsize)
effect_size <- cohens_d(post_score ~ group, data = sample_data)
```

A two-sample t-test revealed a statistically significant difference between groups, t(`r round(t_test_result$parameter, 2)`) = `r round(t_test_result$statistic, 2)`, p `r ifelse(t_test_result$p.value < 0.001, "< 0.001", paste("=", round(t_test_result$p.value, 3)))`, Cohen's d = `r round(effect_size$Cohens_d, 2)`, 95% CI \[`r round(t_test_result$conf.int[1], 2)`, `r round(t_test_result$conf.int[2], 2)`\].

## Secondary Analyses

### Additional Analysis 1

\[Description of additional analysis and results\]

### Additional Analysis 2

\[Description of additional analysis and results\]

## Exploratory Analyses

### Correlation Analysis

```{r}
#| label: fig-correlations
#| fig-cap: "Correlation Matrix of Study Variables"

# Create correlation plot
cor_data <- sample_data %>%
  select(pre_score, post_score, age) %>%
  cor(use = "complete.obs")

corrplot(
  cor_data,
  method = "color",
  type = "upper",
  order = "hclust",
  tl.cex = 0.8,
  tl.col = "black"
)
```

# Discussion

## Summary of Findings

This study investigated \[research focus\] and found several important results:

1.  **Finding 1**: \[Description and interpretation\]
2.  **Finding 2**: \[Description and interpretation\]
3.  **Finding 3**: \[Description and interpretation\]

## Interpretation of Results

### Theoretical Implications

Our findings support \[theoretical position\] and extend previous work by \[extension\]. The results are consistent with \[theory\] which suggests \[theoretical explanation\].

### Practical Implications

These findings have several practical implications:

-   **Implication 1**: \[Description\]
-   **Implication 2**: \[Description\]
-   **Implication 3**: \[Description\]

## Limitations

Several limitations should be considered when interpreting these results:

1.  **Limitation 1**: \[Description and impact\]
2.  **Limitation 2**: \[Description and impact\]
3.  **Limitation 3**: \[Description and impact\]

## Future Directions

Future research should address these limitations and explore:

-   \[Future direction 1\]
-   \[Future direction 2\]
-   \[Future direction 3\]

## Conclusions

In conclusion, this study provides evidence that \[main conclusion\]. The findings contribute to \[field\] by \[contribution\] and have implications for \[applications\]. While limitations exist, the results suggest \[final interpretation\] and support the need for \[recommendations\].

# Acknowledgments

We thank [acknowledgments]. This research was supported by \[funding information\].

# References

::: {#refs}
:::

# Appendices

## Appendix A: Additional Tables

```{r}
#| label: tbl-appendix-a
#| tbl-cap: "Additional Analysis Results"

# Additional table
additional_results <- sample_data %>%
  group_by(group, gender) %>%
  summarise(
    N = n(),
    `Mean Score` = round(mean(post_score), 2),
    `SD` = round(sd(post_score), 2),
    .groups = 'drop'
  )

knitr::kable(additional_results)
```

## Appendix B: Additional Figures

```{r}
#| label: fig-appendix-b
#| fig-cap: "Distribution of Post-test Scores by Group"

sample_data %>%
  ggplot(aes(x = post_score, fill = group)) +
  geom_histogram(alpha = 0.7, bins = 20, position = "identity") +
  facet_wrap(~group, ncol = 1) +
  labs(
    x = "Post-test Score",
    y = "Frequency",
    fill = "Group",
    title = "Distribution of Post-test Scores"
  ) +
  theme_minimal() +
  scale_fill_brewer(type = "qual", palette = "Set2")
```

## Appendix C: R Session Information

```{r}
#| label: session-info
#| echo: true

sessionInfo()
```